\section{Experimental Results}

\Cref{tbl:experiments} displays the results of running \MPass\ tool on  some examples;
whereas in \Cref{tbl:experiments_f}, we show the  results of running \MPass\ on some protocols which are intentionally modified to introduced some errors.
The displayed  examples are   taking  from \cite{JRSVgit}  which are further described in \cite{MPSV11} and \cite{RSV11}.
Bounded Retransmission Protocol (BRP) is also adapted from \cite{AABJ04}.
Columns of both tables should be interpreted as follows:

\begin{inparaenum}
\item {\bf P} lists the names of the protocols under analysis.
\item {\bf Bad} indicates both the process and the state of the process for which the state reachability analysis is conducted.
\item {\bf Sem} indicated the channel semantics used for the analysis: \textit{lossy} (\LCS), \textit{stuttering} (\SLCS) or \textit{unordered} (UCS) channel semantic.
\item {\bf channel} describes how channels are formed.  More precisely, we provide three different ways for defining the channels:
\begin{inparaenum}
\item {\bf xml:}  Channels are specified in the \xml file of the protocol.
\item {\bf prefix:} Channels are constructed based on the first alphabet of the messages.
\item {\bf process:} There is exactly one channel per process.
\end{inparaenum}
We used the \textbf{process} kind of channel specification.
\item {\bf Constraint Generation} (\textbf{Const. Gen.}), \textbf{\SMT} and {\bf Total time} lists, respectively, the time taken to generate  the \SMT-formula,
the time taken by the \SMT\ solver to check the satisfiability of that formula and the total time of the analysis.
\item {\bf Assert} lists the number of assertions fed to the \SMT\ solver,
\item {\bf Ph.} indicated the bound on the number of phases, and finally,
\item {\bf Res} gives the result of the analysis. The results are listed as:
\begin{inparaenum}
\item {\bf U} for Unsafe, i.e. the bad state is reachable (the \SMT\ formula is satisfiable), or
\item {\bf S} for possibly safe, i.e. the bad state is not reachable under the bounded-phase assumption and for the specified channel semantic,
(the \SMT\ formula is unsatisfiable).
\end{inparaenum}
\end{inparaenum}

Results displayed here are for few protocols only. Rest of the results are available online at \cite{github.MPass}
in the \texttt{docs} folder.

\begin{table}
  \begin{center}
    {\scriptsize{
        \begin{tabular}{  |ccc|c|cccc|c|cc|}
        \hline
        \hline
        {\bf P} & {\bf Bad} & {\bf Sem} && {\bf \shortstack{Const. \\ gen.}} & \textbf{\SMT} & {\bf \shortstack{Total \\ time}} & {\bf Assert} && {\bf Ph.} & {\bf Res} \\
        \hline
        \hline
        ABP & \shortstack{RECEIVER Invalid} & UCS && 0.07 sec & 74 sec & 74.07 sec & 4025 && 4 & U(sat) \\ \hline
        ABP & \shortstack{RECEIVER Invalid} & LCS && 0.04 sec & 1 sec & 1.04 sec & 2519 && 3 & S(unsat) \\ \hline
        ABP & \shortstack{RECEIVER Invalid} & SLCS && 0.03 sec & 2 sec & 2.03 sec & 2519 && 3 & S(unsat) \\ \hline
        BRP & \shortstack{RECEIVER Invalid} & UCS && 0.3 sec & 2 sec & 2.3 sec & 23461 && 3 & S(unsat) \\ \hline
        BRP & \shortstack{RECEIVER Invalid} & LCS && 0.28 sec & 2 sec & 2.28 sec & 23461 && 3 & S(unsat) \\ \hline
        BRP & \shortstack{RECEIVER Invalid} & SLCS && 0.28 sec & 1 sec & 1.28 sec & 23461 && 3 & S(unsat) \\ \hline
        STP & \shortstack{A Invalid} & UCS && 0.03 sec & 4 sec & 4.03 sec & 2354 && 6 & U(sat) \\ \hline
        STP & \shortstack{A Invalid} & LCS && 0.02 sec & 0 sec & 0.02 sec & 1348 && 4 & S(unsat) \\ \hline
        STP & \shortstack{A Invalid} & SLCS && 0.02 sec & 0 sec & 0.02 sec & 1348 && 4 & S(unsat) \\ \hline
        \hline
        \end{tabular}} 
    }
  \end{center}
\caption{Verification Results for examples from \cite{MPSV11} and \cite{JRSVgit}}\label{tbl:experiments}
\end{table}

\begin{table}
  \begin{center}
    {\scriptsize{
        \begin{tabular}{ |ccc|c|cccc|c|cc|}
        \hline
        \hline
        {\bf P} & {\bf Bad} & {\bf Sem} && {\bf \shortstack{Const. \\ gen.}} & \textbf{\SMT} & {\bf \shortstack{Total \\ time}} & {\bf Assert} && {\bf Ph.} & {\bf Res} \\
        \hline
        \hline
        ABP\textunderscore F & \shortstack{RECEIVER Invalid} & SLCS &  & 0.04 sec & 1 sec & 1.04 sec & 1275 && 2 & U(sat) \\ \hline
        ABP\textunderscore F & \shortstack{RECEIVER Invalid} & UCS &  & 0.04 sec & 1 sec & 1.04 sec & 1275 && 2 & U(sat) \\ \hline
        SlidingWindow\textunderscore F & \shortstack{RECEIVER Invalid} & SLCS &  & 0.02 sec & 0 sec & 0.02 sec & 913 && 1 & U(sat) \\ \hline
        SlidingWindow\textunderscore F & \shortstack{RECEIVER Invalid} & UCS &  & 0.03 sec & 0 sec & 0.03 sec & 913 && 1 & U(sat) \\ \hline
        Synchronous\textunderscore F & \shortstack{B Invalid} & SLCS &  & 0.02 sec & 0 sec & 0.02 sec & 713 && 3 & U(sat) \\ \hline
        Synchronous\textunderscore F & \shortstack{B Invalid} & UCS &  & 0.02 sec & 0 sec & 0.02 sec & 713 && 3 & U(sat) \\ \hline
        \hline
        \end{tabular}} 
    }
  \end{center}
\caption{Verification Results for buggy (faulty) examples}\label{tbl:experiments_f}
\end{table}